\section{Limitations}
For this project, we face certain limitations when fetching data, because of our lack of expertise in the GraphQL API from GitHub, we had to use the REST API and the amount of requests required is too large for the rate limit imposed by Github API, it took us 4 days to get all the data. 

Github only have one section that has a social aspect which is the issue comments, to improve this research in the future it would require that we use other social networks to evaluate the social aspect of the project, the issue with this is that these social networks would focus on the social aspect of the users and not necessarily of their contributors.

\section{Conclusion}
Open source may appear daunting at first, but working on it will help developers improve their skills and build a support network, each open source community is unique. Each group has its own distinct set of members, each with responsibilities and benefits.

Angular, Vue and Svelte have been increasing in their commits and community, while React has been declining but this would be a sign of maturity rather than a dying project, after all, is back by Facebook and it's an integral part of their ecosystem.

We also layout a potential use case for the project and how the community analysis could be improved to better depict how the communities interact outside of GitHub.

\pagebreak

\section{Reflections}
We begin this project with the precognition that we would be able to categorize each project into a particular bucket, that each community would have their own signature on how they are structured and it makes it different from one another, but in the end, they are all very similar, it doesn't matter if are projects backed by big companies, like React or Angular, or small projects that started with a single developer like Vue or Svelte.

In the end, this community is positive and really professional in their development, and the core contributors look willing to help newcomers, one thing that we noticed is that all these projects have a code of conduct that help all the participants in the community to align with the core values of the project and that permeates all their contributors.

\pagebreak
